Project Equalizer

### 2006-10-05 WhitePapers/ProjectEqualizer/paper.tex
minor documentation (project status) update

% how/when
The open development approach of Equalizer maximizes the benefits for
hardware vendors, software developers, research institutions and end
users. Interested parties are strongly encouraged to contact us. We are
looking for contributions or founding for several components of Equalizer.
}
\vfill
{\center\begin{tabularx}{.88\textwidth}{|l|l|X|}
\hline
\bf Version & \bf Date & \bf Changes \\
\hline
0.1         & July 5, 2006   & Initial Draft\\
\hline
\multicolumn{3}{c}{\small Latest version at 
  \htmladdnormallink{http://www.equalizergraphics.com/documents/ProjectEqualizer.pdf}
  {http://www.equalizergraphics.com/documents/ProjectEqualizer.pdf}}\\
\end{tabularx}}
\clearpage
\pagenumbering{arabic}

@@

By the end of 2006, the programming framework will be developed to a
usable state for the development of commercial multipipe applications by
an experienced OpenGL programmer. This includes some scalability modes
to show the benefits of scalable rendering on commodity graphics clusters.

@@

\subsection{Programming Framework}
The core part of the Equalizer project is the programming framework and
resource server. Naturally, these two components are the first major
milestone. Currently, they are usable to start the development of
parallel graphics applications. Both the server and the client library
miss major functionality, particularly decomposition modes.

>>>>

% how/when
The open development approach of Equalizer maximizes the benefits for
hardware vendors, software developers, research institutions and end
users. Interested parties are strongly encouraged to contact us. We are
looking for contributions or founding for several components of Equalizer.
}
\vfill
{\center\begin{tabularx}{.88\textwidth}{|l|l|X|}
\hline
\bf Version & \bf Date & \bf Changes \\
\hline
0.2         & October 5, 2006 & update status\\
0.1         & July 5, 2006    & initial draft\\
\hline
\multicolumn{3}{c}{\small Latest version at 
  \htmladdnormallink{http://www.equalizergraphics.com/documents/ProjectEqualizer.pdf}
  {http://www.equalizergraphics.com/documents/ProjectEqualizer.pdf}}\\
\end{tabularx}}
\clearpage
\pagenumbering{arabic}

@@

Currently, the programming framework is usable for the development of
commercial multipipe applications by an experienced OpenGL
programmer. By the end of 2006, we will have implemented the core
scalable rendering engine to show the benefits of scalable rendering on
commodity graphics clusters.

@@

\subsection{Programming Framework}
The core part of the Equalizer project is the programming framework and
resource server. Naturally, these two components are the first major
milestone. Currently, they are usable to start the development of
parallel graphics applications. Right now Equalizer supports multipipe
rendering for display walls and immersive virtual reality installations,
including stereo and head tracking.
